Typed Functional Genetic Programming

### 2013-07-30 tex/thesis.tex
uterý 4:07

Desired type of generated programs $\sigma$ and 
building blocks context $\Gamma$ are following.
\newcommand{\Real}{\mathbb{R}}
\begin{align*}
\sigma = \Real \ar &\Real\\
\Gamma = \{
  (+)  &: \Real \ar \Real \ar \Real    ,\\
  (-)  &: \Real \ar \Real \ar \Real    ,\\
  (*)  &: \Real \ar \Real \ar \Real    ,\\
  rdiv &: \Real \ar \Real \ar \Real    ,\\
  sin  &: \Real \ar \Real              ,\\
  cos  &: \Real \ar \Real              ,\\
  exp  &: \Real \ar \Real              ,\\ 
  rlog &: \Real \ar \Real              \}\\
\end{align*}

@@

\section{Artificial Ant}

@@

The Santa Fe trail lies on toroidal square grid and has following layout.

~\\~[ TODO OBRAZEK Santa Fe]\\

@@

TODO asi přenda do future work

>>>>

Desired type of generated programs $\sigma$ and 
building blocks context $\Gamma$ are following.
\newcommand{\Real}{\mathbb{R}}
\begin{align*}
\sigma = \Real \ar &\Real\\
\Gamma = \{
  (+)  &: \Real \ar \Real \ar \Real    ,\\
  (-)  &: \Real \ar \Real \ar \Real    ,\\
  (*)  &: \Real \ar \Real \ar \Real    ,\\
  rdiv &: \Real \ar \Real \ar \Real    ,\\
  sin  &: \Real \ar \Real              ,\\
  cos  &: \Real \ar \Real              ,\\
  exp  &: \Real \ar \Real              ,\\ 
  rlog &: \Real \ar \Real              \}\\
\end{align*}
where
\begin{align*}
rdiv(p,q) &= \begin{cases} 1 &\mbox{if } q = 0 \\
p/q & \mbox{otherwise } \end{cases}  \\
rlog(x) &= \begin{cases} 0 &\mbox{if } x = 0 \\
log(\vert x\vert) & \mbox{otherwise}. \end{cases}
\end{align*}

@@

\newpage
\section{Artificial Ant}

@@

The Santa Fe trail lies on toroidal square grid.
The ant is in the upper left corner, facing right.
It has following layout.

\includegraphics[scale=1]{santafe.png}

@@
